---
title: "MA678 Midterm Project"
author: "Yujia Wang"
date: "December 12, 2021"
output:
  pdf_document: 
          latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
# set up the environment
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, highlight=FALSE)
knitr::opts_chunk$set(fig.width=6, fig.height=5,fig.align="center") 
```

```{r}
# source my code
source("MidtermProject_Draft.R")
```


## Abstract

xxx 

## Introduction

xxx
https://www.kaggle.com/debajyotipodder/co2-emission-by-vehicles?select=CO2+Emissions_Canada.csv
https://open.canada.ca/data/en/dataset/98f1a129-f628-4ce4-b24d-6f16bf24dd64/resource/026e45b4-eb63-451f-b34f-d9308ea3a3d9?inner_span=True

## Method

### Data Cleaning and Combining

xxx

|column names                     |explanation|
|:--:                             |:-----|
|Make                             |Company of the vehicle|
|Model                            |Car Model|
|VehicleClass                     |Class of vehicle depending on their utility, capacity and weight|
|EngineSize                       |Size of engine used in Litre|
|Cylinders                        |Number of cylinders|
|Transmission                     |Transmission type with number of gears|
|FuelType                         |Type of Fuel used|
|FC_City                          |Fuel consumption in city roads (L/100 km)|
|FC_Hwy                           |Fuel consumption in highways (L/100 km)|
|FC_Comb                          |The combined fuel consumption (55% city, 45% highway) in L/100 km|
|CO2Emissions                     |The tailpipe emissions of carbon dioxide (in grams per kilometre) for combined city and highway driving|

xxx

### Exploratory Data Analysis

xxx 

```{r, fig.height=5, fig.width=10, fig.cap="xxx"}
# variable "Make" barplot
make_barplot
```

xxx 

```{r, fig.height=5, fig.width=10, fig.cap="xxx"}
# "co2" boxplot
co2_boxplot
```

xxx

```{r, fig.height=7, fig.width=14, fig.cap="xxx"}
# stack plot: VehicleClass, EngineSize, Cylinders, Transmission, FuelType 

```

### Model Fitting

```{r}

# # estimate result
# summary(model2)
# 
# # coefficient
# coef(model)
# 
# # fix effect
# fixef(model)
# 
# # random effect
# ranef(model)
# 
# 
# 
# random_fueltype <- as.data.frame(ranef(model2)$FuelType)
# random_transmission <- as.data.frame(ranef(model2)$Transmission)

```










### Model checking

```{r}
# full fitting model1 result
HLM_summary(model1)
```

```{r}
# full fitting model2 result
HLM_summary(model2)
```

```{r}
# residual plot and Q-Q plot
grid.arrange(re1,qq1,re2,qq2,nrow=2)
```

```{r}
# random effect

plot_model(model1,type="re",show.values=TRUE,value.offset=.2,vline.color = "black",facet.grid=FALSE,sort.est = "sort.all")

plot_model(model2,type="re",show.values=TRUE,value.offset=.2,vline.color = "black",facet.grid=FALSE,sort.est = "sort.all")


```




xxx



## Result

## Model Coefficients

xxx

$$log(comments)= -12.70 + 0.77\cdot log(duration) + 0.32\cdot log(views) + 2.15\cdot log(numlang)$$

xxx

### Model Validation

```{r}

```

   
xxx

## Discussion

xxx





## Reference

https://stat.ethz.ch/~meier/teaching/anova/random-and-mixed-effects-models.html

https://psych252.github.io/psych252book/linear-mixed-effects-models-2.html 

https://www.r-bloggers.com/2020/02/a-guide-to-encoding-categorical-features-using-r/

\newpage
## Appendix







