---
title: "MA678 Midterm Project"
author: "Yujia Wang"
date: "December 2, 2021"
output:
  pdf_document: 
          latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
# set up
knitr::opts_chunk$set(echo=TRUE,
                      out.width="0.9\\linewidth",
                      dev="png",
                      fig.align='center',
                      message = FALSE,
                      warning = FALSE)
pacman::p_load(ggplot2,
               knitr,
               arm,
               data.table,
               stringr,
               rstan,
               rstanarm,
               readr,
               tidyverse)
```

```{r,echo=FALSE}
CO2 <- read.csv("CO2EmissionsCanada.csv", header = T)
```

## Abstract

xxx 

## Introduction

xxx

## Method

### Data Cleaning and Processing

xxx

| column names      | explanation |
| :--:              | :----- |
| title             | The title of talk|
| num_lang          | The number of available languages translations |
| comments          | The number of comments |
| duration_ted      | How long is the  video in  seconds |
| view_ted          | The number of views |
| categories        | The video was under which category on YouTube|
| english           | Indicate the native language is English or not|

xxx

### Exploratory Data Analysis

```{r, echo=FALSE}

```

xxx  

```{r, echo=FALSE, fig.height=4, fig.width= 10,fig.cap="xxx"}
ggplot
```

### Model Fitting

```{r, echo=FALSE}

```

xxx

|                |Estimate   |Std. Error  |df        |t value |Pr(>&#124;t&#124;) |
|:---:           |:---:      |:---:       |:---:     |:---:   |:---:              |
|(Intercept)     |-12.93     |0.67        |16.75     |-19.43  |6.34e-13 ***       |
|log_duration    |0.79       |0.04        |24.53     |17.57   |2.10e-15 ***       |
|log_views       |0.33       |0.04        |12.21     |8.09    |2.99e-06 ***       |
|log_numlang     |2.33       |0.13        |10.98     |18.56   |1.21e-09 ***       |

## Result

## Model Coefficients

xxx

$$log(comments)= -12.70 + 0.77\cdot log(duration) + 0.32\cdot log(views) + 2.15\cdot log(numlang)$$

xxx

|                        |(Intercept) |log_duration |log_views  |log_numlang |
|:---:                   |:---:       |:---:        |:---:      |:---:       |
|Entertainment           |-12.70      |0.77         |0.32       |2.15        |
|News & Politics         |-14.37      |0.90         |0.38       |2.21        |
|People & Blogs          |-12.28      |0.73         |0.37       |2.47        |
|Science & Technology    |-13.37      |0.82         |0.21       |2.49        |

### Model Validation

```{r, echo=FALSE}

```
   
xxx

## Discussion

xxx

## Citation

xxx    

\newpage
## Appendix
### More EDA
```{r, echo=FALSE}

```





\newpage





