---
title: "MA678 Midterm Project"
author: "Yujia Wang"
date: "December 10, 2021"
output:
  pdf_document: 
          latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
# set up
knitr::opts_chunk$set(echo=TRUE,
                      out.width="0.9\\linewidth",
                      dev="png",
                      fig.align='center',
                      message = FALSE,
                      warning = FALSE)
# library
pacman::p_load(ggplot2,
               knitr,
               arm,
               dplyr,
               stringr,
               rstan,
               rstanarm,
               readr,
               tidyverse,
               hrbrthemes,
               corrplot,
               lmer,
               lmer4,
               lattice,
               gridExtra)
```

## Abstract

xxx 

## Introduction

xxx
https://www.kaggle.com/debajyotipodder/co2-emission-by-vehicles?select=CO2+Emissions_Canada.csv
https://open.canada.ca/data/en/dataset/98f1a129-f628-4ce4-b24d-6f16bf24dd64/resource/026e45b4-eb63-451f-b34f-d9308ea3a3d9?inner_span=True

## Method

### Data Cleaning and Combining

```{r, echo=FALSE}
# import two dataset
co2 <- read.csv("CO2EmissionsCanada.csv", header = T)
battery <- read.csv("MY2012-2021BatteryElectricVehicles.csv", header = T)
# clean "battery" dataset
battery <- battery[-c(1),c(2,3,4,6,7,11,12,13,15)]
battery <- battery %>%
  add_column(Engine.Size.L="NA")
battery <- battery %>%
  add_column(Cylinders="NA")
battery <- battery[,c(1,2,3,10,11,4,5,6,7,8,9)]
colnames(battery) <- c("Make","Model","VehicleClass","EngineSize","Cylinders","Transmission","FuelType","FC_City","FC_Hwy","FC_Comb","CO2Emissions")
battery <- battery[order(battery$Make),]
battery <- distinct(battery,Make,Model,VehicleClass,.keep_all=TRUE)
battery <- transform(battery,EngineSize=as.numeric(EngineSize),
                             Cylinders=as.integer(Cylinders),
                             FC_City=as.numeric(FC_City),
                             FC_Hwy=as.numeric(FC_Hwy),
                             FC_Comb=as.numeric(FC_Comb),
                             CO2Emissions=as.integer(CO2Emissions))
battery <- mutate(battery,Make=toupper(Make),Model=toupper(Model),VehicleClass=toupper(VehicleClass))

# clean "co2" dataset
co2 <- co2[,-c(11)]
colnames(co2) <- c("Make","Model","VehicleClass","EngineSize","Cylinders","Transmission","FuelType","FC_City","FC_Hwy","FC_Comb","CO2Emissions")
# combine two dataset
identical(names(co2), names(battery))
co2_final <- rbind(co2,battery)
co2_final <- co2_final[order(co2_final$Make),]
```

xxx

|column names                     |explanation|
|:--:                             |:-----|
|Make                             |Company of the vehicle|
|Model                            |Car Model|
|VehicleClass                     |Class of vehicle depending on their utility, capacity and weight|
|EngineSize                       |Size of engine used in Litre|
|Cylinders                        |Number of cylinders|
|Transmission                     |Transmission type with number of gears|
|FuelType                         |Type of Fuel used|
|FC_City                          |Fuel consumption in city roads (L/100 km)|
|FC_Hwy                           |Fuel consumption in highways (L/100 km)|
|FC_Comb                          |The combined fuel consumption (55% city, 45% highway) is shown in L/100 km|
|CO2Emissions                     |The tailpipe emissions of carbon dioxide (in grams per kilometre) for combined city and highway driving|

xxx

### Exploratory Data Analysis

xxx 

```{r, echo=FALSE}
# calculate "Make" amount
Make_data <- co2_final %>% 
  group_by(Make) %>% summarise(Count = n())
```

```{r, echo=FALSE, fig.height=7, fig.width=14, fig.cap="xxx"}
# variable "Make" barplot
ggplot(data=Make_data, aes(x=Make, y=Count)) +
  geom_bar(stat='identity', fill=rainbow(n=length(Make_data$Count))) +
  theme(axis.text.x=element_text(angle=90, vjust=0.7), plot.title=element_text(size=15)) +
  labs(x="Brand", y="Amount of vehicle", title="The amount of vehicle in different brands")
```

xxx 

```{r, echo=FALSE, fig.height=7, fig.width=14, fig.cap="xxx"}
# "co2" boxplot
ggplot(data=co2_final, aes(x=Make, y=,CO2Emissions, fill=Make)) + 
    geom_boxplot() +
    theme(axis.text.x=element_text(angle=90, vjust=0.7), legend.position='none') +
    labs(x="Brand", y="CO2 emission", title="The CO2 emission of vehicle in different brands")
```

xxx

```{r, echo=FALSE, fig.height=7, fig.width=14, fig.cap="xxx"}
# distribution of CO2 emissions histogram
ggplot(data=co2_final, aes(x=CO2Emissions)) +
    geom_histogram(aes(y=..density..),binwidth=5, fill="#666666", color="#e9ecef") +
    geom_density(lwd=1.5,linetype=1,colour="#FF0033") +
    theme(plot.title=element_text(size=15)) +
    labs(x="CO2 emissions", y="Count", title="Distribution of CO2 emissions")
```

xxx

```{r, echo=FALSE}
# prepare for corrplot
Corrplot_data <- co2_final[,-c(1,2,3,6,7)]
Corrplot_data <- transform(Corrplot_data,
                             FC_City=as.numeric(FC_City),
                             FC_Hwy=as.numeric(FC_Hwy),
                             FC_Comb=as.numeric(FC_Comb),
                             CO2Emissions=as.numeric(CO2Emissions))
Corrplot_data_final <- cor(Corrplot_data, use =  "complete.obs")
round(Corrplot_data_final,2)
```

```{r, echo=FALSE, fig.height=7, fig.width=14, fig.cap="xxx"}
corrplot(Corrplot_data_final, type="upper", order="hclust", tl.col="black", tl.srt=45)
```

xxx

```{r, echo=FALSE}
# prepare for the pie plot
Percent_data_1 <- co2_final %>% 
  group_by(VehicleClass) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(percent=`n`/sum(`n`)) 
Percent_data_1$label <- scales::percent(Percent_data_1$percent)

Percent_data_2 <- co2_final %>% 
  group_by(EngineSize) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(percent=`n`/sum(`n`)) 
Percent_data_2$label <- scales::percent(Percent_data_2$percent)

Percent_data_3 <- co2_final %>% 
  group_by(Cylinders) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(percent=`n`/sum(`n`)) 
Percent_data_3$label <- scales::percent(Percent_data_3$percent)

Percent_data_4 <- co2_final %>% 
  group_by(Transmission) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(percent=`n`/sum(`n`)) 
Percent_data_4$label <- scales::percent(Percent_data_4$percent)

Percent_data_5 <- co2_final %>% 
  group_by(FuelType) %>% 
  count() %>% 
  ungroup() %>% 
  mutate(percent=`n`/sum(`n`)) 
Percent_data_5$label <- scales::percent(Percent_data_5$percent)
```

```{r, echo=FALSE, fig.height=7, fig.width=14, fig.cap="xxx"}
# pie plot: VehicleClass, EngineSize, Cylinders, Transmission, FuelType 
ggplot(data=Percent_data_1)+
  geom_bar(aes(x="", y=percent, fill=VehicleClass), stat="identity", width = 1)+
  coord_polar("y", start=0, direction = -1)+
  theme_void()+
  geom_text(aes(x=1, y = cumsum(percent)-percent/2), label=Percent_data_1$label)

ggplot(data=Percent_data_2)+
  geom_bar(aes(x="", y=percent, fill=EngineSize), stat="identity", width = 1)+
  coord_polar("y", start=0, direction = -1)+
  theme_void()+
  geom_text(aes(x=1, y = cumsum(percent)-percent/2), label=Percent_data_2$label)

ggplot(data=Percent_data_3)+
  geom_bar(aes(x="", y=percent, fill=Cylinders), stat="identity", width = 1)+
  coord_polar("y", start=0, direction = -1)+
  theme_void()+
  geom_text(aes(x=1, y = cumsum(percent)-percent/2), label=Percent_data_3$label)

ggplot(data=Percent_data_4)+
  geom_bar(aes(x="", y=percent, fill=Transmission), stat="identity", width = 1)+
  coord_polar("y", start=0, direction = -1)+
  theme_void()+
  geom_text(aes(x=1, y = cumsum(percent)-percent/2), label=Percent_data_4$label)

ggplot(data=Percent_data_5)+
  geom_bar(aes(x="", y=percent, fill=FuelType), stat="identity", width = 1)+
  coord_polar("y", start=0, direction = -1)+
  theme_void()+
  geom_text(aes(x=1, y = cumsum(percent)-percent/2), label=Percent_data_5$label)
```

### Model Fitting

```{r, echo=FALSE}
co2_final <- transform(co2_final,Make=as.factor(Make),
                                 Model=as.factor(Model),
                                 VehicleClass=as.factor(VehicleClass),
                                 EngineSize=as.factor(EngineSize),
                                 Cylinders=as.factor(Cylinders),
                                 Transmission=as.factor(Transmission),
                                 FuelType=as.factor(FuelType))
# just a test
model_test <- lmer(CO2Emissions~EngineSize+FuelType+FC_Comb+(1|Make ),data=co2_final)
summary(model_test)
# can't add more: fixed-effect model matrix is rank deficient so dropping 1 column / coefficient
```


```{r, echo=FALSE}
# zero
model0 <- lmer(CO2Emissions~(1|FuelType ),data=co2_final)
summary(model0)

#
model1 <- lmer(CO2Emissions~Cylinders+(1|FuelType ),data=co2_final)
summary(model1)

#
AIC(model0)
BIC(model0)
deviance(model0,REML=FALSE)
AIC(model1)
BIC(model1)
deviance(model1,REML=FALSE)


library("lmerTest")
#install.packages("bruceR")
library("bruceR")
HLM_summary(fit)

#install.packages("MuMIn")
library("MuMIn")


fit <- lmer(CO2Emissions~FC_City+FC_Hwy+FC_Comb+(1+FC_Comb|FuelType),data=co2_final)
#+(1+log_duration|categories)+(1+log_views|categories)+(1+log_numlang|categories)
coef(fit)
summary(fit)

anova( , , )
install.packages("texreg")
library("texreg")
texreg::screenreg(list( , , ))
```
|Make                       
|Model                       
|VehicleClass                
|EngineSize                      
|Cylinders                    
|Transmission            
|FuelType                       
|FC_City                      
|FC_Hwy                       
|FC_Comb         
|CO2Emissions 

xxx

```{r}
# complete pooling
ggplot(co2_final)+geom_point()+aes(x=Cylinders,y=CO2Emissions)+geom_smooth(method="lm",se=FALSE)

# no pooling
ggplot(co2_final)+geom_point()+aes(x=FuelType,y=CO2Emissions,color=factor(Make))+geom_smooth(method="lm",se=FALSE)+facet_wrap(~Make)

```

## Result

## Model Coefficients

xxx

$$log(comments)= -12.70 + 0.77\cdot log(duration) + 0.32\cdot log(views) + 2.15\cdot log(numlang)$$

xxx

### Model Validation

```{r echo=FALSE, fig.height=2.5, fig.width=6, fig.cap="Residual plot and Q-Q plot."}
#binnedplot(fitted(fit4),resid(fit4))
re <- plot(fit)
qq <- qqmath(fit)
grid.arrange(re,qq,nrow=1)
```

```{r echo=FALSE, fig.height=2, fig.width=4, fig.cap="Residuals vs Leverage."}
ggplot(data.frame(lev=hatvalues(fit4),pearson=residuals(fit4,type="pearson")),
      aes(x=lev,y=pearson)) +
    geom_point() +
    theme_bw()
```
   
xxx

## Discussion

xxx

## Citation

xxx    

\newpage
## Appendix
```{r, echo=FALSE}
# scatter plot matrices
#install.packages("psych")
library("psych")
pairs.panels(co2_final)
```






