---
title: "MA678 Midterm Project"
author: "Yujia Wang"
date: "December 2, 2021"
output:
  pdf_document: 
          latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
# set up
knitr::opts_chunk$set(echo=TRUE,
                      out.width="0.9\\linewidth",
                      dev="png",
                      fig.align='center',
                      message = FALSE,
                      warning = FALSE)
pacman::p_load(ggplot2,
               knitr,
               arm,
#              data.table,
               dplyr,
               stringr,
               rstan,
               rstanarm,
               readr,
               tidyverse)
```

## Abstract

xxx 

## Introduction

xxx
https://www.kaggle.com/debajyotipodder/co2-emission-by-vehicles?select=CO2+Emissions_Canada.csv
https://open.canada.ca/data/en/dataset/98f1a129-f628-4ce4-b24d-6f16bf24dd64/resource/026e45b4-eb63-451f-b34f-d9308ea3a3d9?inner_span=True

## Method

### Data Cleaning and Combining

```{r, echo=FALSE}
# import data
co2 <- read.csv("CO2EmissionsCanada.csv", header = T)
battery <- read.csv("MY2012-2021BatteryElectricVehicles.csv", header = T)
# data explore
str(co2)
distinct(co2,Make)
distinct(battery,Make)
# process battery
battery1 <- 
battery2 <- 
# process co2


# combine

```

xxx

|column names                     |explanation|
|:--:                             |:-----|
|Make                             |Company of the vehicle|
|Model                            |Car Model|
|Vehicle.Class                    |Class of vehicle depending on their utility, capacity and weight|
|Engine.Size.L                    |Size of engine used in Litre|
|Cylinders                        |Number of cylinders|
|Transmission                     |Transmission type with number of gears|
|Fuel.Type                        |Type of Fuel used|
|Fuel.Consumption.City..L.100 km. |Fuel consumption in city roads (L/100 km)|
|Fuel.Consumption.Hwy..L.100.km.  |Fuel consumption in highways (L/100 km)|
|Fuel.Consumption.Comb..L.100.km. |The combined fuel consumption (55% city, 45% highway) is shown in L/100 km|
|Fuel.Consumption.Comb..mpg.      |The combined fuel consumption in both city and highway is shown in mile per gallon(mpg)|
|CO2.Emissions.g.km.              |The tailpipe emissions of carbon dioxide (in grams per kilometre) for combined city and highway driving|

xxx

### Exploratory Data Analysis

```{r, echo=FALSE}

```

xxx  

```{r, echo=FALSE, fig.height=4, fig.width= 10,fig.cap="xxx"}
#ggplot
```

### Model Fitting

```{r, echo=FALSE}

```

xxx

|                |Estimate   |Std. Error  |df        |t value |Pr(>&#124;t&#124;) |
|:---:           |:---:      |:---:       |:---:     |:---:   |:---:              |
|(Intercept)     |-12.93     |0.67        |16.75     |-19.43  |6.34e-13 ***       |
|log_duration    |0.79       |0.04        |24.53     |17.57   |2.10e-15 ***       |
|log_views       |0.33       |0.04        |12.21     |8.09    |2.99e-06 ***       |
|log_numlang     |2.33       |0.13        |10.98     |18.56   |1.21e-09 ***       |

## Result

## Model Coefficients

xxx

$$log(comments)= -12.70 + 0.77\cdot log(duration) + 0.32\cdot log(views) + 2.15\cdot log(numlang)$$

xxx

|                        |(Intercept) |log_duration |log_views  |log_numlang |
|:---:                   |:---:       |:---:        |:---:      |:---:       |
|Entertainment           |-12.70      |0.77         |0.32       |2.15        |
|News & Politics         |-14.37      |0.90         |0.38       |2.21        |
|People & Blogs          |-12.28      |0.73         |0.37       |2.47        |
|Science & Technology    |-13.37      |0.82         |0.21       |2.49        |

### Model Validation

```{r, echo=FALSE}

```
   
xxx

## Discussion

xxx

## Citation

xxx    

\newpage
## Appendix
```{r, echo=FALSE}

```












